---
title: "Simulation Study Summary Report"
output: html_document
---

# Background

Performed a simulation study to compare the performance of three estimators (mean, trimmed mean, and median) of the population mean by comparing their BIAS and MSE. 

# Results

See table below for BIAS and MSE results.  

```{r,echo=FALSE}
# Set to location of .RData file from Topic 6 Part 3
in_dir <- "/Users/meganneely/Dropbox/Duke Teaching/BIOS 721/2_Lectures/Topic7_ReproResearchR/Part 2/" 
in_dir <- ""
# Load the R Workspace with the simulation results
# - Should sit the fit objects listed in the workspace
#   after running the load() command
load(paste(in_dir,'sim_allns_fitobjects.RData',sep=''))

# Function to create each row in table shell
make.row <- function(fit.object,prop){
  which.prop <- which(seq(0,0.2,by=0.01)==prop)
  cell1 <- paste(formatC(fit.object$bias.t1[which.prop],digits=3,format='f'),
                 ' (',
                 formatC(fit.object$mse.t1[which.prop],digits=3,format='f'),
                 ')',sep='')
  cell2 <- paste(formatC(fit.object$bias.t2[which.prop],digits=3,format='f'),
                 ' (',
                 formatC(fit.object$mse.t2[which.prop],digits=3,format='f'),
                 ')',sep='')
  cell3 <- paste(formatC(fit.object$bias.t3[which.prop],digits=3,format='f'),
                 ' (',
                 formatC(fit.object$mse.t3[which.prop],digits=3,format='f'),
                 ')',sep='')
  row <- c(cell1,cell2,cell3)
  return(list(row=row))}

# Create a data objec that mirrors the table shell 
table.object <- NULL 

sampsize.n50 <- rep(NA,3)            # Section 1 of Table Shell 
table.object <- rbind(table.object,sampsize.n50)

prop.out.00 <- make.row(fit.n50,0)$row
table.object <- rbind(table.object,prop.out.00)

prop.out.05 <- make.row(fit.n50,0.05)$row
table.object <- rbind(table.object,prop.out.05)

prop.out.10 <- make.row(fit.n50,0.10)$row
table.object <- rbind(table.object,prop.out.10)

sampsize.n100 <- rep(NA,3)           # Section 2 of Table Shell 
table.object <- rbind(table.object,sampsize.n100)

prop.out.00 <- make.row(fit.n100,0)$row
table.object <- rbind(table.object,prop.out.00)

prop.out.05 <- make.row(fit.n100,0.05)$row
table.object <- rbind(table.object,prop.out.05)

prop.out.10 <- make.row(fit.n100,0.10)$row
table.object <- rbind(table.object,prop.out.10)

sampsize.n150 <- rep(NA,3)           # Section 3 of Table Shell 
table.object <- rbind(table.object,sampsize.n150)

prop.out.00 <- make.row(fit.n150,0)$row
table.object <- rbind(table.object,prop.out.00)

prop.out.05 <- make.row(fit.n150,0.05)$row
table.object <- rbind(table.object,prop.out.05)

prop.out.10 <- make.row(fit.n150,0.10)$row
table.object <- rbind(table.object,prop.out.10)

colnames(table.object) <- c('Mean','20% Trimmed Mean','Median')
```

Table 1. Bias and Mean Square Error of Estimators for the Population Mean [^tab.foot]

[^tab.foot]: Results reported as Bias (Mean Square Error); Bias and Mean Square Error based on average over 1000 simulation runs. 

| | **Mean** | **20% Trimmed Mean** | **Median** |
|:---------------|:---------------:|:---------------:|:---------------:|
| **Sample Size = 50**  | | | |
| % Outliers = 0        | `r table.object[2,1]`  | `r table.object[2,2]`  | `r table.object[2,3]`  |
| % Outliers = 5        | `r table.object[3,1]`  | `r table.object[3,2]`  | `r table.object[3,3]`  |
| % Outliers = 10       | `r table.object[4,1]`  | `r table.object[4,2]`  | `r table.object[4,3]`  |
| **Sample Size = 100** | | | |
| % Outliers = 0        | `r table.object[6,1]`  | `r table.object[6,2]`  | `r table.object[6,3]`  |
| % Outliers = 5        | `r table.object[7,1]`  | `r table.object[7,2]`  | `r table.object[7,3]`  |
| % Outliers = 10       | `r table.object[8,1]`  | `r table.object[8,2]`  | `r table.object[8,3]`  |
| **Sample Size = 150** | | | |
| % Outliers = 0        | `r table.object[10,1]` | `r table.object[10,2]` | `r table.object[10,3]` |
| % Outliers = 5        | `r table.object[11,1]` | `r table.object[11,2]` | `r table.object[11,3]` |
| % Outliers = 10       | `r table.object[12,1]` | `r table.object[12,2]` | `r table.object[12,3]` |

<!-- This is this sytanx for a COMMENT in RMarkdown --> 

<!--
Table 1. Bias and Mean Square Error of Estimators for the Population Mean [^tab.foot]

[^tab.foot]: Results reported as Bias (Mean Square Error); Bias and Mean Square Error based on average over 1000 simulation runs. 
-->

``` {r, echo=FALSE,eval=FALSE}
library(knitr)
kable(table.object,
      align=c('l','c','c','c'))
```

# Conclusions

Mean is superior when proportion of outliers is low (< 5%), but the median becomes superior as the proportion increases. However, for higher proportions the performance of all three estimators suffers.  
